---
title: "Project 2: Collegiate CSV file"
output:
  html_document:
    pandoc_args: [
      "+RTS", "-K64m",
      "-RTS"
    ]
---
For analysis, we are using a database of US college financial aid information made available through the US Department of Education College Affordability and Transparency Center. We hope to visualize some trends present in current college financial aid distributions throughout the nation. "Null" data points represent statstics that were unreported by their respective universities.

###Reproducing Our Work:
1. Create a GitHub repository for the project.
2. Create the folders for your project.
3. Find a csv file for statistical comparisons. Our CSV file was obtained by selecting the appropriate options from the website: http://collegecost.ed.gov/catc/Default.aspx
4. Clean up variable names using "college data wranging.r" file and use output to create SQL table in SQL Developer.
5. Import CSV into SQL Developer
6. Build an html file to document these steps.

Before generating plots, we run the 'require.r' file to make sure the necessary packages are in place.
```{r}
source("../require.R")
```

###Summary and Subset:
The SQL used on the table selects all colleges where the tutition and fees for the 2013-2014 academic year were not zero. This selection means that schools such as the "United States Air Force Academy" were not included in this analysis because they do not have tutition and fees.
```{r, echo=TRUE}
source("../01 Data/summary.R", echo = TRUE)
```

###Plot #1:
SQL used to isolate the data for this dataframe selected the entire table and excluded universities with tutition and fee values for the 2013-2014 academic year of zero dollars.

This plot uses some advanced piping techniques in R including the use of the cumulative distribution function. The visualization shows the average dollar amount of institutional grant money offered to college freshmen broken down by percentile vs. the school's tuition and fees for the 2013-2014 academic school year.

Before analyzing this visualization, it is important to note that our data includes 1216 private not-for-profit schools, 560 public schools, and 303 private-for-profit schools.

There are several things going on in this first visualization. In the bottom quartile of the data, there are more private-for-profit universities than any other type of university. Private not-for-profit universities seem to appear in least frequency in the top quartile of the data. In the top half of the data, there appear to be more public universities than any other type of university.

Questions that arise from this visualization include:
1. Public universities seem to be offering institutional grants worth more than private not-for-profit universities, despite the fact that most all private not-for-profit schools have higher tuition and fees than their public counterparts. Are private not-for-profit universities overcharging for their services?

2. Private for-profit universities seem to appear most often in the top half of all universities, meaning they offer fairly weighty grants  to their freshmen, but their tuition and fees are not as high as not-for-profit colleges. What's going on here?

```{r}
source("../02 Data Wrangling/plot1.R", echo = TRUE)
```


